Tesseroids: command-line tools for gravity field forward modeling in spherical coordinates

### 2014-03-28 manuscript.tex
Better shell fig and figs with tess splitting
Made a figure with examples of splitting a tesseroid using different
ratios.

In shell figure, removed parallels and meridians and made whole shell
discretized into tesseroids.

Using relative paths for both figures in Inkscape.
Added figure of tesseroid in coord system
Also added a caption to the split figure.
Caption for tesseroid figure

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid}
    \caption{
        View of a tesseroid,
        the integration point $Q$,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$.
    }
    \label{fig:tesseroid}
\end{figure}

This is a reference to Figure~\ref{fig:tesseroid}.

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/tesseroid-split.png}
    \caption{
        Adaptive discretization for a computation point P
        of the tesseroid shown in (a) using distance/size ratios of
        (b) 0.5, (c) 1, and (d) 2.
        $d$ is the distance between the tesseroid and P.
    }
    \label{fig:split}
\end{figure}

This is a reference to Figure~\ref{fig:split}.
